Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-15 paper/main.tex
Made some spaces before \cite

\subsubsection{NIST evaluation criteria for SHA-3}

\label{sec:lengthextension}
\paragraph{Security.} The most important criterion for the SHA-3
candidates is security\cite{s_nistround2}. \citet{s_fedreg} lays out the full
description of security criteria, however the most noteworthy criterion
in regards to Tahoe-\ac{LAFS} is that \ac{SHA}-3 candidates are required to have
resistance against length-extension attacks. Both \ac{SHA}-1 and the \ac{SHA}-2
family are vulnerable to this kind of attack, and thus requires
Tahoe to run the algorithm twice, as described by \citet{schneier}.

\paragraph{Cost and Performance.} Cost and Performance are considered to be the
second most important criterion. The absolute minimum for performance is that
the SHA-3 candidate should be faster than the functions in the \ac{SHA}-2
family\cite{s_nistround2}.  Cost is a measure of how much memory an
implementation requires in software, both the implementation itself and the use
of \ac{RAM} during runtime. Another measure of cost is how many logic gates it
takes to implement the function in hardware.

@@

\vspace{12pt}
Based on these criteria, we choose the fastest possible implementation based on
our benchmark in \ac{SUPERCOP} \cite{s_tahoe_supercop}. The relative speed of
each implementation, in relation to other implementation for the same and other
candidates can be found at eBASH\cite{s_tahoe_supercop}.

>>>>

\subsubsection{NIST evaluation criteria for SHA-3}
\label{sec:lengthextension}

\paragraph{Security.} The most important criterion for the SHA-3
candidates is security \cite{s_nistround2}. \citet{s_fedreg} lays out the full
description of security criteria, however the most noteworthy criterion
in regards to Tahoe-\ac{LAFS} is that \ac{SHA}-3 candidates are required to have
resistance against length-extension attacks. Both \ac{SHA}-1 and the \ac{SHA}-2
family are vulnerable to this kind of attack, and thus requires
Tahoe to run the algorithm twice, as described by \citet{schneier}.

\paragraph{Cost and Performance.} Cost and Performance are considered to be the
second most important criterion. The absolute minimum for performance is that
the SHA-3 candidate should be faster than the functions in the \ac{SHA}-2
family \cite{s_nistround2}.  Cost is a measure of how much memory an
implementation requires in software, both the implementation itself and the use
of \ac{RAM} during runtime. Another measure of cost is how many logic gates it
takes to implement the function in hardware.

@@

\vspace{12pt}
Based on these criteria, we choose the fastest possible implementation based on
our benchmark in \ac{SUPERCOP} \cite{s_tahoe_supercop}. The relative speed of
each implementation, in relation to other implementation for the same and other
candidates can be found at eBASH \cite{s_tahoe_supercop}.
